\section*{Sammanfattning} %unnumbered
Detta är \textit{User Requirements Document 1} för \textit{The Meta Family}'s projekt i kursen Mjukvarukonstruktion. Projektets syfte är att skapa ett \textit{Software Development Kit} (SDK) för beta-testning av applikationer till Android. Beställaren av projektet, \textit{The Beta Family}, har en motsvarande SDK till iOS som detta projekt ämnar att replikera. Det befintliga SDK:t dokumenterar användarens upplevelser av applikationen för att ge utvecklaren återkoppling.

Dokumentet ska ge en uttömmande beskrivning av de användarkrav som framställts. I dokumentet presenteras relevanta tekniska och praktiska begränsningar. Dokumentet följer standarden PSS-05.

\section*{Abstract}
This is the \textit{User Requirements Document 1} of \textit{The Meta Family}s project in the course \textit{Introduction to Software Engineering}. The purpose of the project is to create a \textit{Software Development Kit} (SDK) for beta-testing of applications for Android devices. The customer of the project, \textit{The Beta Family}, have an equivalent SDK released for iOS, which this project is intend to replicate. The released SDK records the user's experience of the application in order to provide feedback to the developer.

This document is meant to provide a comprehensive description of the user requirements provided by the customer. Relevant technical and practical constraints are presented and considered. The document follows the PSS-05 document standard.
